In-Band Synchronization for\\Distributed SDN Control Planes\thanks{Supported by the European Research Council (ERC) Starting Grant no.~259085, the European Institute of Innovation \& Technology (EIT) project 13153 (Software Defined Networking) and the FP7 EU project UNIFY.}

### 2015-12-06 ccr-camera/inband-sync.tex
fixed camera submission issues. submitted again.

%\documentclass[11pt]{llncs}
%\documentclass[11pt,pdftex]{article}
%\documentclass{sig-alternate-10pt}
%\usepackage{amsthm}
%\usepackage{algorithm}
%\usepackage[noend]{algorithmic}

@@

\author{
Liron Schiff$^1$  \quad % \thanks{Supported by the European Research Council (ERC) Starting Grant no. 259085 and by the Israel Science Foundation Grant no.~1386/11.} $^1$,
Stefan Schmid$^2$ \quad Petr Kuznetsov$^3$ \\
\small $^1$ Tel Aviv University, Israel \quad $^2$ Aalborg University,
Denmark \quad $^3$ T\'el\'ecom ParisTech, France
}

>>>>

\pdfpageheight 11in
\pdfpagewidth 8.5in
%\documentclass[11pt]{llncs}
%\documentclass[11pt,pdftex]{article}
%\documentclass{sig-alternate-10pt}
%\usepackage{amsthm}
%\usepackage{algorithm}
%\usepackage[noend]{algorithmic}

@@

\numberofauthors{3}
\author{
\alignauthor Liron Schiff \\
\affaddr{Tel Aviv University, Israel} \\
%\affaddr{ACM} \\
%\affaddr{New York, NY} \\
%\email{griscti@hq.acm.org}
\alignauthor Stefan Schmid \\
\affaddr{Aalborg University, Denmark} \\
%\affaddr{ACM} \\
%\affaddr{New York, NY} \\
%\email{murray@hq.acm.org}
\alignauthor Petr Kuznetsov \\
\affaddr{T\'el\'ecom ParisTech, France} \\
%\affaddr{ACM} \\
%\affaddr{New York, NY} \\
%\email{rous@hq.acm.org}
}
%\author{
%Liron Schiff$^1$  \quad % \thanks{Supported by the European Research Council (ERC) Starting Grant no. 259085 and by the Israel Science Foundation Grant no.~1386/11.} $^1$,
%Stefan Schmid$^2$ \quad Petr Kuznetsov$^3$ \\
%\small $^1$ Tel Aviv University, Israel \quad $^2$ Aalborg University,
%Denmark \quad $^3$ T\'el\'ecom ParisTech, France
%}
